Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-11 WRITEUP/ms.tex
manual obtained from overleaf

\usepackage{amsmath}
\input{preamble}
\slugcomment{To be Submitted.}

@@

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini\altaffilmark{3, 4}}
\author{Andrea Ferrara\altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7}}

@@

\section{Introduction}%\label{sec:intro}

\AP{i have to check abstract and Sections 3. 4. 5., in particular 5.2; check also what have been moved to the app}

The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes) and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material. The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves are more gas-rich in their star-forming molecular gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability and lead
to the formation of gas structures that are typically more massive and denser than those
observed in nearby galaxies, with masses of $M_{\rm cl}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the
migration of such giant massive clumps are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

This paper is structured as follows.
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{eqn}, we present the formalism within which we interpret the results.
In \Sec{results}, we present scaling relations for the MCs identified. 
% Toomre stability analysis in \Sec{Q}.
We then interpret the results   % , robustness of our analysis, caveats,
and discuss the implications of our findings in \Sec{diss},
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

% ------------------
\section{Simulation and Method} \label{sec:sim}

\subsection{\ncode{Serra} Simulation\footnote{Serra means greenhouse in Italian which is motivated by the
fact that our simulation includes a chemical network to calculate the abundance of H$_2$, which in turn
dictates the formation of CO.
}}
The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.

\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the main advantages for studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    Star formation history of \flower (top right) and
    projected stellar mass distribution of \flower during 
    {\it (a)} one of its accretion phases
    at its early stage of evolution; 
    {\it (b)} one of its major starburst phases
    after a major merger; and
    {\it (c)} a relatively quiescent phase post-starburst.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

We show the \SF history of \flower in \Fig{SFH},
where the SFR is calculated based on existing young stellar population, which is
defined to have an age of $t_{\rm age}<$\,10\,Myr.
The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from
massive satellite galaxies within the surrounding $\approx$50\,kpc, which
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to
a starburst phase after a major merger, and then back to a relatively quiescent phase,
over the few hundred Myr simulated in the simulation.

Given the stochasticity in the \SF history of \flower (see \Fig{SFH}),
we show the scaling relations found for two snapshots, corresponding to two of its most extreme evolutionary stages,
in \Sec{singless} to illustrate the salient points of the discussion presented in this paper.
The two phases (when \flower is accreting materials from its surrounding 
and when \flower is undergoing a major starburst phase) are expected to bracket the most extreme variations in the cloud dynamics.

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
In the customized version used for this study, we modify the function to enhance the stability of the code.
% (which essentially means we fixed the bugs in order for it to actually work).

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
We note that, owing to the nature of \obs, such structures are identified
in position-position-velocity (PPV) space, whereas in simulations, one has the
full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical properties extracted in
PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a,
Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot, corresponding to the
accretion phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
    Color shows the H$_2$ surface density, weighted by the column density.
%   \AP{plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density
where ``clumps/structures'' are
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).}
to the same snapshot
used to plot \Fig{h2density}.

@@

Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

\section{Basic Physics} \label{sec:eqn}
\subsection{Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% \AP{I fear that putting this subsection here breaks a bit the flow of the analysis of the results. Maybe we can put it as an appendix and keep only eq. 10 in the main text (a put it at when analysing the relevant plot)? }

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:alpha}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation),
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes:
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

We use the virial parameter, which is defined by \Eq{alpha} and describes
the balance between kinetic and gravitational potential energies,
to quantify how stable an MC is.
An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms
and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that
the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.

\subsection{Gravitational Instabilities}   \label{sec:Q}
The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
From virial theorem, Jeans 
instability sets the scales at which gravitational potential overcomes kinetic energy. Namely, gravitational instabilities 
dominates at scales $L > L_J$, where $L_J$ is the Jeans length. 
However, centrifugal force resulting from differential rotation in disk galaxies can 
inhibit collapse even on these scales. As a result, a disk is thought to be 
unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
% \propto \Sigma/B^2
by the surface density of the disk and the angular velocity of the rotation.

>>>>

\usepackage{amsmath}

\usepackage{comment}

\input{preamble}
\slugcomment{To be Submitted.}

@@

\author{T. K. Daisy Leung\altaffilmark{1,2}}
\author{Andrea Pallottini\altaffilmark{3,4}}
\author{Andrea Ferrara\altaffilmark{4,5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2,6,7}}

@@

\section{Introduction}

\AP{i have to check abstract and Section 5., in particular 5.2; check also what have been moved to the app}

\AP{For some plots, still the old versions are the ones available. It might still be overleaf fault. An option would be to have a clean new overleaf document; pros: probably the compilation will be faster and the service less buggy (e.g. selecting every time the main manuscript file, files are actually uploaded, etc) and thus more convenient to use; cons: it will not be syncronized with the repo}

The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes) and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material. The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves are more gas-rich in their star-forming molecular gas contents compared to present-day galaxies.
%
These massive gas inflows in turn trigger gravitational instability and lead
to the formation of gas structures that are typically more massive and denser than those
observed in nearby galaxies, with masses of $M_{\rm cl}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the
migration of such giant massive clumps are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

%This paper is structured as follows. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower), and describe the method used to identify its molecular gas complexes. In \Sec{eqn}, we present the formalism within which we interpret the results. In \Sec{results}, we present scaling relations for the MCs identified. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and present our conclusions in \Sec{conclusion}.
This paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results. In \Sec{results}, we present the results and the scaling relations for the MCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%

% ------------------
\section{Numerical simulations} \label{sec:sim}

\subsection{\ncode{Serra} Simulation\footnote{Serra means greenhouse in Italian which is motivated by the
fact that our simulation includes a chemical network to calculate the abundance of H$_2$, which in turn
dictates the formation of CO.
}}

The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.
%
\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend. Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
%
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}. Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the main advantages for studying the dynamical properties of molecular structures at $z$\ssim6 in simulation is the fact that we can examine how their properties evolve as a function of time.
%
This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF. Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

\begin{figure*}[!htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    Star formation history of \flower (top right) and projected stellar mass distribution of \flower during {\it (a)} one of its accretion phases at its early stage of evolution; {\it (b)} one of its major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.\AP{please rearrange the maps such that either i) they have an L shape ii) they are all bewlo the SFR; numbers on the axis are too small, and phase (a) is missing the colorbar; a single colorbar for the star maps might substitute the current 2 ones; please use magma colorbar for the maps (or in any case the colorbar that has been select for for $\Sigma$ trhought the paper)}
\label{fig:SFH}}
\end{figure*}

We show the \SF history of \flower in \Fig{SFH}, where the SFR is calculated based on existing young stellar population, which is defined to have an age of $t_{\rm age}<$\,10\,Myr. The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher than shown here since they also include contributions from massive satellite galaxies within the surrounding $\approx$15\,kpc ($\simeq$ to the virial radius).} as it evolves from an actively accreting phase to a starburst phase after a major merger, and then back to a relatively quiescent phase, over the few hundred Myr simulated in the simulation.

Given the stochasticity in the \SF history of \flower (see \Fig{SFH}), in \Sec{singless} \AP{but we both give the analysis for 2 stages for maps and all the stages in the scaling relation, is it correct? if so, this point should be made clearer here (or in the next section)} our work is focused on the analysis of two of its most extreme evolutionary stages, to illustrate the salient points of the discussion presented in this paper. The two phases correspond to i) when \flower is accreting materials from its surrounding  and ii) when \flower is undergoing a major starburst phase; such pahses are expected to bracket the most extreme variations in the cloud dynamics.

\section{Molecular Cloud Complexes}\label{sec:eqn}

\subsection{Structure identification}\label{sec:method}

To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. In the customized version used for this study, we modify the function to enhance the stability of the code.
% (which essentially means we fixed the bugs in order for it to actually work).

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2). We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying ``clumps'' based on/after applying $\sigma$-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).

We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single evolutionary stage, corresponding to the accretion phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see text). Color shows the H$_2$ surface density, weighted by the column density. \AP{I would use the label $n_{\rm H2}$ instead of $n({\rm H2})$; i would add the corresponding $n_{cut}= ...$ in withe the lower right corner of each right panel; in the caption I would add which stage is the figure extracted from; optionally, the 3 row might be substituted by a single row with cuts of different colors (if yt allows ...)}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower~for a given evolutionary stage which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{\AP{i would move this note to the (main text of the) section introducing althaea}For reference, the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times the critical density of the Universe is $r_{\rm 200}$\ssim15\,kpc.}.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}). We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).} to the same stage used to plot \Fig{h2density}.

@@

Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

%\subsection{Key Properties of Clouds}
\subsection{Properties of the Clouds}

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as mass (\AP{we should uniform the notation} $M_{\rm cl}$), effective size ($R$), \AP{introduced here but not used except for comparison with vallini (in the text); maybe we can remove it} Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate the non-thermal component of the velocity dispersion (\AP{check the definitions, we are using multiple symbols to indicate the same things} $\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC. \AP{I would first introduce the velocity dispersion and the separate them in thermal and non thermal component; also, even $c_s$ is density weighted average} The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here. \AP{isn t this definition already given in the main text?} In the subsequent sections, we adopt the root mean square of the velocity field as the velocity dispersion ($\sigma$). \label{ftn:veldisp}}. On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MC distributions in terms of their molecular gas masses, radii, and gas mass fractions, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass withing the MC volume.
%
We note that the distributions vary for different evolutionary stage of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{6.5}$\,\Msun for the densest MC.
%
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the considered evolutionary stages for each of the given $n_{\rm cut}$ (see \Sec{method}). The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.7\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{Distributions of mass, size, and gas mass fraction of MCs identified using the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
%
Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified at higher $n_{\rm cut}$.
\AP{it is a bit difficult to read the xaxis label; an option (but i'm not sure if it will work) would be to have a 3x2 alignment, and keeping the same axis range for both cuts (for easier visual comparison)}
\label{fig:dist}}
\end{figure*}

%\section{Basic physical properties}\label{sec:eqn}

%\subsection{Virial Equilibrium and Larson's Relations}\label{sec:PVE}
\subsection{Larson's Relations}\label{sec:PVE}

In next sections, we examine and compare properties of the MCs with observations in the context of the Larson's relations \citep{Larson81a}. Namely, the linewidth-size, density-size, and mass-size relations. Larson's relations are adopted for the discussion in this work as they  describe the interactions between gravity and turbulence, and is the first set of relations used for studying star-forming molecular structure formation based on observables which has been routinely used for comparing properties of molecular structures in different galactic environments.
% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
